The Bug Catalog of the Maven Ecosystem

### 2014-02-20 docs/msr.tex
working on data collection

First, we scanned the Maven repository only
for appropriate {\sc jar}s and created a list that included them.
This is because FindBugs analyzes applications written in Java,
and the Maven repository hosts projects from
languages other than Java such as Scala, Groovy,
Clojure, etc. Thus we filtered out such projects.
In particular, we obtained a snapshot (January 2012) of
the repository and handled it locally to retrieve a list of all
the names of the Java project versions that existed in it.
The statistic measurements concerning the repository can be seen in 
Table~\ref{tbl:repository}.

>>>>

The data collection process started with the mirroring of the Maven repository.
The repository typically contains the {\sc jar} files with sources and binary distributions, 
{\sc xml} metadata files that contain the version list for each project and its dependencies and one 
metadata file, also in {\sc xml} format, with specific data for each version.

We exported a list of all the {\sc jar} files in the repository and initially we excluded those
that contained the source distribution for the projects. Then we kept all those {\sc jar}s that 
referred to Java projects, because Findbugs analyzes only applications written in Java,
and the Maven repository hosts projects from languages other than Java such as Scala, Groovy,
Clojure, etc.

The initial snapshot of the repository was obtained in January 2012 and those experinment took
place in the end of 2012. In the meantime, several versions were released for some of the selected project.
We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
the missing ones.

The whole process produced a file list with all the valid {\sc jar} files for our experinment.

In particular, we obtained a snapshot (January 2012) of
the repository and handled it locally to retrieve a list of all
the names of the Java project versions that existed in it.
The statistic measurements concerning the repository can be seen in 
Table~\ref{tbl:repository}.
